### 2016-06-21 templates/report/scientific_mission/tex/scientific_missions.tex
NIRA-96 - Create latex reports for the Activity app Created latex reports for seminars and training programs.
Code optimization

{% autoescape off %}{% block content %}\begin{longtable}{ |p{4cm}|p{5,4cm}|p{2cm}|p{1,8cm}|p{1,8cm}| }
\hline
Researcher & Scientific mission & Local & Start date & End date \\ \hline
{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} &{{ mission.destination_city }} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
\end{longtable}

{% endblock %}
{% endautoescape %}

>>>>

{% autoescape off %}{% block content %}\begin{longtable}{ |p{4cm}|p{5,4cm}|p{2cm}|p{1,8cm}|p{1,8cm}| }
\hline
Researcher & Scientific mission & Local & Start date & End date \\ \hline
{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} & {% if mission.destination_city.country.name == 'Brazil' %}{{ mission.destination_city.name }} - {{ mission.destination_city.region.alternate_names }}{% else %}{{ mission.destination_city.name }}, {{ mission.destination_city.country }}{% endif %} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
\end{longtable}{% endblock %}{% endautoescape %}
